\thispagestyle{empty}
We have written this set of unofficial notes to facilitate your understanding of important concepts in Probability Theory. Although most parts of the notes are based the lecture videos and in-person lectures given by Prof. Igor Krasovsky in Spring 2022, we have included additional materials drawn from various references. In particular: 

\begin{unexaminable}
\begin{itemize}
    \item first-time readers may skip the materials in the grey-coloured boxes. These materials are not typically examined in the Probability Theory course offered at Imperial, and are usually not covered in lectures (although this might not be true for similar courses offered at other universities).
\end{itemize}
\end{unexaminable}
\begin{itemize}
    \item Any unfinished/planned materials are written in \red{red}.
\end{itemize}

\textbf{Disclaimer.} These notes have not been checked by Dr. Krasovsky and should not be regarded as a replacement of the official notes and lectures for the course. In particular, all the errors are made by us, and we don't take any responsibility for their consequences; use at your own risk (and please do attend lectures -- they are fun). \\

\textbf{License.} The work is \textbf{currently} subject to Creative Common Attribution 4.0 International (CC BY 4.0) license. (\url{https://creativecommons.org/licenses/by/4.0/legalcode}) You are free to share and/or adapt the work, on condition of 
\begin{itemize}
    \item giving appropriate credit to the lecturer, Prof. Igor Krasovsky. You may do so in any reasonable manner, but not in any way that suggests the licensor endorses you or your use.
    \item retain the link to the license,
    \item not applying legal terms or technological measures that legally restrict others from doing anything the license permits.
\end{itemize}
The license may change in line with the college regulations.\\

Please email us at (insert email) with any comments or corrections.\\

Finally, we would like to congratulate Prof. Krasovsky in his recent tenureship.\\

Ivan Kirev and Samuel Lam \\
February 2023

\newpage 

\tableofcontents
\newpage

\pagestyle{fancy}

